\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-03 papers/jfp/10-conclusions.tex
Restore acknowledgements

>>>>

\section*{Acknowledgements}

Thanks to anonymous reviewers and everyone else who provided us with feedback
on earlier drafts: Ulf Adams, Arseniy Alekseyev, Dan Bentley, Martin
Br\"{u}stel, Ulan Degenbaev, Jeremie Dimino, Andrew Fitzgibbon, Georgy
Lukyanov, Simon Marlow, Evan Martin, Yaron Minsky, Guillaume Maudoux, Philip
Patsch, Michael Peyton Jones, Andrew Phillips, Fran\c{c}ois Pottier, Rohit
Ramesh, Irakli Safareli, Zhen Zhang. Your contributions were incredibly
valuable.

Andrey Mokhov is funded by a Royal Society Industry Fellowship \cmd{IF160117}
on the topic ``Towards Cloud Build Systems with Dynamic Dependency Graphs''.
